---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

3) Do you observe differences in coordination between conditions? Report the models and results.

4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?

```{r setup, include=FALSE}
library(lmerTest);library(ggplot2) ;library(caret); library(pastecs); library(lsr); library(crqa);library(magrittr); library(dplyr); library(tidyr); library(pacman); library(groupdata2); library(stringr); library(readr)
p1t1 = read.csv("CleanData/Study2_G5_T1_Synchronous.csv")
p1t2 = read.csv("CleanData/Study2_G5_T2_TurnTaking.csv")
p1t3 = read.csv("CleanData/Study2_G5_T3_Conversation.csv")

#Plotting respiration
ggplot(p1t1, aes(time, Resp1)) + geom_line(color = "blue") + geom_line(aes(x=time, y = Resp2, color = "red")) + theme(legend.position = "none")
ggplot(p1t2, aes(time, Resp1)) + geom_line(color = "blue") + geom_line(aes(x=time, y = Resp2, color = "red")) + theme(legend.position = "none")
ggplot(p1t2, aes(time, Resp1)) + geom_line(color = "blue") + geom_line(aes(x=time, y = Resp2, color = "red")) + theme(legend.position = "none")

#Plotting heartrate
ggplot(p1t1, aes(time, HR1)) + geom_line(color = "blue") + geom_line(aes(x=time, y = HR2, color = "chartreuse4")) + theme(legend.position = "none")
ggplot(p1t2, aes(time, HR1)) + geom_line(color = "blue") + geom_line(aes(x=time, y = HR2, color = "chartreuse4")) + theme(legend.position = "none")
ggplot(p1t2, aes(time, HR1)) + geom_line(color = "blue") + geom_line(aes(x=time, y = HR2, color = "chartreuse4")) + theme(legend.position = "none")


#Downsample the data
p1t1 = p1t1 %>% group(n= 100, method= 'greedy') %>% dplyr::summarise(time= mean(time,na.rm=T),        
                   HR1 = mean(HR1,na.rm=T),       
                   HR2 = mean(HR2,na.rm=T),       
                   Resp1 = mean(Resp1,na.rm=T),       
                   Resp2 = mean(Resp2,na.rm=T))
p1t2 = p1t2 %>% group(n= 100, method= 'greedy') %>% dplyr::summarise(time= mean(time,na.rm=T),        
                   HR1 = mean(HR1,na.rm=T),       
                   HR2 = mean(HR2,na.rm=T),       
                   Resp1 = mean(Resp1,na.rm=T),       
                   Resp2 = mean(Resp2,na.rm=T))
p1t3 = p1t3 %>% group(n= 100, method= 'greedy') %>% dplyr::summarise(time= mean(time,na.rm=T),        
                   HR1 = mean(HR1,na.rm=T),       
                   HR2 = mean(HR2,na.rm=T),       
                   Resp1 = mean(Resp1,na.rm=T),       
                   Resp2 = mean(Resp2,na.rm=T))
#Outlier function
removeOuts <- function(ts,threshold){
  ts[ts > (mean(ts,na.rm=T) +              (threshold*sd(ts,na.rm=T))) |  ts < (mean(ts,na.rm=T) -           (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)   
  return(ts)}
threshold=2.5 

#Outlier removal
p1t1$HR1=removeOuts(p1t1$HR1,threshold)
p1t1$HR2=removeOuts(p1t1$HR2,threshold)  
p1t1$Resp1=removeOuts(p1t1$Resp1,threshold)
p1t1$Resp2=removeOuts(p1t1$Resp2,threshold)

p1t2$HR1=removeOuts(p1t2$HR1,threshold)
p1t2$HR2=removeOuts(p1t2$HR2,threshold)  
p1t2$Resp1=removeOuts(p1t2$Resp1,threshold)
p1t2$Resp2=removeOuts(p1t2$Resp2,threshold)

p1t3$HR1=removeOuts(p1t3$HR1,threshold)
p1t3$HR2=removeOuts(p1t3$HR2,threshold)  
p1t3$Resp1=removeOuts(p1t3$Resp1,threshold)
p1t3$Resp2=removeOuts(p1t3$Resp2,threshold)
  

#Scaling the signals: 
p1t1$Resp1S=scale(p1t1$Resp1)  
p1t1$Resp2S=scale(p1t1$Resp2)  
p1t1$HR1S=scale(p1t1$HR1) 
p1t1$HR2S=scale(p1t1$HR2)

p1t2$Resp1S=scale(p1t2$Resp1)  
p1t2$Resp2S=scale(p1t2$Resp2)  
p1t2$HR1S=scale(p1t2$HR1) 
p1t2$HR2S=scale(p1t2$HR2)

p1t3$Resp1S=scale(p1t3$Resp1)  
p1t3$Resp2S=scale(p1t3$Resp2)  
p1t3$HR1S=scale(p1t3$HR1) 
p1t3$HR2S=scale(p1t3$HR2)

#Plotting respiration with scaled data
plot1 = ggplot(p1t1, aes(time, Resp1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y = Resp2S, color = "red")) + theme(legend.position = "none")
plot2 = ggplot(p1t2, aes(time, Resp1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y = Resp2S, color = "red")) + theme(legend.position = "none")
plot3 = ggplot(p1t2, aes(time, Resp1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y = Resp2S, color = "red")) + theme(legend.position = "none")

# To make one grid with all respiration plots
gridExtra::grid.arrange(plot1, plot2, plot3)

#Plotting heartrate with scaled data 
plot4 = ggplot(p1t1, aes(time, HR1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y = HR2S, color = "chartreuse4")) + theme(legend.position = "none")
plot5 = ggplot(p1t2, aes(time, HR1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y = HR2S, color = "chartreuse4")) + theme(legend.position = "none")
plot6 = ggplot(p1t2, aes(time, HR1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y = HR2S, color = "chartreuse4")) + theme(legend.position = "none")

# To make one grid with all heartrate plots
gridExtra::grid.arrange(plot4, plot5, plot6)


#For the respiration plots it seems, by eye-ball, that the first condition, the synchronous condition have more coordinated respiration. The other two conditions, turn-taking and conversation, seem to be opposite of each other and not coordinated. 
#For the heartrate plots the same pattern occurs. 
  
#Running crqa
par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip") 

#Creating a loop 

files = list(p1t1, p1t2, p1t3)

Dimension_resp = NULL
Radius_resp = NULL
Delay_resp = NULL
Dimension_HR = NULL
Radius_HR = NULL
Delay_HR = NULL
n = 1

for (file in files) {
  ans_Resp = try(optimizeParam(file$Resp1S, file$Resp2S, par, min.rec = 2, max.rec = 8))
  ans_HR = try(optimizeParam(file$HR1S, file$HR2S, par, min.rec = 2, max.rec = 8))
  if (length(ans_Resp) > 1) {
  
  Dimension_resp[n] = ans_Resp$emddim
  Radius_resp[n] = ans_Resp$radius
  Delay_resp[n] = ans_Resp$delay
  }
  
  else {
    Dimension_resp[n] = NA
    Radius_resp[n] = NA
    Delay_resp[n] = NA
  }
  
  if (length(ans_HR) > 1) {
  
  Dimension_HR[n] = ans_HR$emddim
  Radius_HR[n] = ans_HR$radius
  Delay_HR[n] = ans_HR$delay
  }
  
  else {
    Dimension_HR[n] = NA
    Radius_HR[n] = NA
    Delay_HR[n] = NA
  }
n=n+1

}

param_resp = data.frame(Dimension_resp, Radius_resp, Delay_resp, Dimension_HR, Radius_HR, Delay_HR)

mean(param_resp$Dimension, na.rm = TRUE) # 2
mean(param_resp$Delay, na.rm = TRUE) # 28
mean(param_resp$Radius, na.rm = TRUE) # 0.38

#Results for synchronous condition:
Results_sync=crqa (p1t1$Resp1S, p1t1$Resp2S, delay= 28, embed= 2, radius= 0.38, normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

#To plot the results in a recurrence plot
RP = Results_sync$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white","blue4") 
image(RP, xlab = "", ylab = "", col = cols)


#Explore the lags of coordination:
Profile=drpdfromts(p1t1$Resp1S, p1t1$Resp2S,datatype = 'continuous',ws=50,radius=0.44)
timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
maxlag = Profile$maxlag/1000
profile = Profile$profile*100
Prof=data.frame(profile)
ggplot(Prof, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[maxlag], colour='red') 


#Results for turn taking condition:
Results_turn=crqa (p1t2$Resp1S, p1t2$Resp2S, delay= 28, embed= 2, radius= 0.38, normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

#To plot the results in a recurrence plot
RP = Results_turn$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white","blue4") 
image(RP, xlab = "", ylab = "", col = cols)

#Explore the lags of coordination:
Profile=drpdfromts(p1t2$Resp1S, p1t2$Resp2S,datatype = 'continuous',ws=50,radius=0.38)
timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
maxlag = Profile$maxlag/1000
profile = Profile$profile*100
Prof=data.frame(profile)
ggplot(Prof, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[maxlag], colour='red') 

#Results for conversation condition:
Results_conv=crqa (p1t3$Resp1S, p1t3$Resp2S, delay= 28, embed= 2, radius= 0.38, normalize=0,rescale=0,mindiagline = 2,minvertline = 2)

#To plot the results in a recurrence plot
RP = Results_conv$RP
RP = matrix(as.numeric(RP), nrow = ncol(RP))
cols = c("white","blue4") 
image(RP, xlab = "", ylab = "", col = cols)

#Explore the lags of coordination:
Profile=drpdfromts(p1t3$Resp1S, p1t3$Resp2S,datatype = 'continuous',ws=50,radius=0.44)
timecourse = round( seq(-5000,5000,100)/1000, digit = 1)
maxlag = Profile$maxlag/1000
profile = Profile$profile*100
Prof=data.frame(profile)
ggplot(Prof, aes(timecourse,profile))+geom_line()+ geom_vline(xintercept = timecourse[maxlag], colour='red') 

```

### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.
- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.
```{r setup, include=FALSE}

filelist = list.files(path="CleanData", pattern = ".csv")

preprocess = function(data){
  data = data%>%    
  group(n= 100, method= 'greedy') %>%    
  dplyr::summarise(time= mean(time,na.rm=T),        
                   HR1 = mean(HR1,na.rm=T),       
                   HR2 = mean(HR2,na.rm=T),       
                   Resp1 = mean(Resp1,na.rm=T),       
                   Resp2 = mean(Resp2,na.rm=T))
#Outlier removal
  data$HR1=removeOuts(data$HR1,threshold)
  data$HR2=removeOuts(data$HR2,threshold)
  data$Resp1=removeOuts(data$Resp1,threshold)
  data$Resp2=removeOuts(data$Resp2,threshold)

#Scaling the signals: 
  data$Resp1S=scale(data$Resp1)  
  data$Resp2S=scale(data$Resp2)  
  data$HR1S=scale(data$HR1) 
  data$HR2S=scale(data$HR2)
  
  return(data)
}


#To create a loop to preprocess all data
finaldata = data.frame()
n = 1 

for (file in filelist) {
  data1=read_csv(paste0("Cleandata/",file))
  
  datafile=preprocess(data1)
  
  datafile$filename = filelist[n]
  write.csv(datafile, file = paste0(file))
  
  par = list(lgM =  50, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 40, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip") 


  ans_Resp = try(optimizeParam(datafile$Resp1S, datafile$Resp2S, par, min.rec = 2, max.rec = 8))
    if (length(ans_Resp) > 1) {
    
    datafile$Dimension_resp = ans_Resp$emddim
    datafile$Radius_resp = ans_Resp$radius
    datafile$Delay_resp = ans_Resp$delay
    }
    else {
      datafile$Dimension_resp = NA
      datafile$Radius_resp = NA
      datafile$Delay_resp = NA
    }
  
  ans_HR = try(optimizeParam(datafile$HR1S, datafile$HR2S, par, min.rec = 2, max.rec = 8))
    if (length(ans_HR) > 1) {
    datafile$Dimension_HR = ans_HR$emddim
    datafile$Radius_HR = ans_HR$radius
    datafile$Delay_HR = ans_HR$delay
    }
    
    else {
      datafile$Dimension_HR = NA
      datafile$Radius_HR = NA
      datafile$Delay_HR = NA
    }
  
  
  finaldata = rbind(finaldata, datafile)
  
  Resp_plot= ggplot(datafile, aes(x=time, y= Resp1S)) + geom_line(color = "red") + geom_line(aes(x=time, y=Resp2S), color = "blue")
  
  HR_plot = ggplot(datafile, aes(x=time, y= HR1S)) + geom_line(color = "purple") + geom_line(aes(x=time, y=HR2S), color = "chartreuse4")
  
  final_plot=gridExtra::grid.arrange(Resp_plot, HR_plot)
  
  ggsave(paste0(file, ".png"), plot = final_plot, path = "Plot")
  
  n=n+1
} 


# To get column with study number

for (file in 1:nrow(finaldata)){
  if (grepl("Study1", finaldata$filename[file])){
    finaldata$Study[file] = 1}
  if (grepl("Study2", finaldata$filename[file])){
    finaldata$Study[file] = 2}
}

# To get group number
finaldata$Group=regmatches(finaldata$filename, regexpr("[G].*[0-9]", finaldata$filename))

finaldata$Group = gsub("[G, _, T]", "", finaldata$Group)

finaldata$Group=substr(finaldata$Group, 1, nchar(finaldata$Group)-1)

# To get trial number
finaldata$Trial=regmatches(finaldata$filename, regexpr("[T].*[0-9]", finaldata$filename))

finaldata$Trial = gsub("[T]", "", finaldata$Trial)

# To get condition
finaldata = finaldata %>% group_by(filename) %>% mutate(Condition = gsub('.{4}$', '', strsplit(filename, "_")[[1]][4]))


# To remove files with "useless" data: Study1G1T1, Study1G1T2, Study1G2T1, Study1G2T2
finaldata = finaldata[finaldata$filename !="Study1_G1_T1_Synchronous.csv",]
finaldata = finaldata[finaldata$filename !="Study1_G1_T2_TurnTaking.csv",]
finaldata = finaldata[finaldata$filename !="Study1_G2_T1_TurnTaking.csv",]
finaldata = finaldata[finaldata$filename !="Study1_G2_T2_Synchronous.csv",]

#Write to csv
write.csv(finaldata, "finaldata.csv")

finaldata = read.csv("finaldata.csv")
finaldata = finaldata[-1:-2]
finaldata = finaldata[-2:-5]

# To get mean parameters for CRQA
mean(finaldata$Dimension_resp, na.rm = TRUE) # 3.19 = 3
mean(finaldata$Radius_resp, na.rm = TRUE) # 0.614
mean(finaldata$Delay_resp, na.rm = TRUE) # 29.463 = 29

mean(finaldata$Dimension_HR, na.rm = TRUE) # 11.9497 = 12 
mean(finaldata$Radius_HR, na.rm = TRUE) # 1.6333
mean(finaldata$Delay_HR, na.rm = TRUE) # 29.8855 = 30

# - Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

#To run crqa
CRQA = function(data) {
  RespCRQA = crqa(data$Resp1S, data$Resp2S, delay = 29, embed = 3,
                   radius = 0.8, normalize = 0, rescale = 0,
                   mindiagline = 2, minvertline = 2)
  RespCRQA$RP = NULL  # Remove large matrix
  RespCRQA = as_tibble(RespCRQA) %>%
    mutate(type = 'Resp')
  
  HrCRQA = crqa(data$HR1S, data$HR2S, delay = 30, embed = 12,
                radius = 2.6, normalize = 0, rescale = 0,
                mindiagline = 2, minvertline = 2)
  HrCRQA$RP = NULL  # Remove large matrix
  HrCRQA = as_tibble(HrCRQA) %>%
    mutate(type = 'HR')
  
  return(rbind(RespCRQA, HrCRQA))
  
}


crqa_results = finaldata %>%
  #dplyr::select(-c(.groups)) %>%  # Remove .groups (not needed right?)
  dplyr::group_by(filename) %>%  # Group by each file
  dplyr::do(CRQA(.)) %>%  # Do CRQA on each group (file)
  dplyr::ungroup()  # Ungroup (prob. not needed, didn't check) 

#Checking the value of RR to regulate radius
mean(crqa_results$RR)

finaldata2 = merge(crqa_results, finaldata, by = "filename")

write.csv(finaldata2, "finaldata2.csv")

finaldata2 = read.csv("finaldata2.csv")
finaldata2 = finaldata2[-1]
```
### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs
 
```{r setup, include=FALSE}

filelist3 = list.files(path = "PreprocessedData", pattern = ".csv")
CRQA_shuffled = data.frame()
n=1

for (file in filelist3) {
  d=read_csv(paste0("PreprocessedData/",file))
  #Sample function shuffles the results
  d$HR1S = sample(d$HR1S)
  d$HR2S = sample(d$HR2S)
  d$Resp1S = sample(d$Resp1S)
  d$Resp2S = sample(d$Resp2S)
  
  data=CRQA(d)
  
  data$filename = filelist3[n]
  
  CRQA_shuffled=rbind(data, CRQA_shuffled)
  
  n=n+1
  
}

finaldata2 = finaldata2[-1]
crqa_results$CRQA = "Normal"
CRQA_shuffled$CRQA = "Shuffled"
CRQA_data = rbind(crqa_results,CRQA_shuffled)

CRQA_HR = subset(CRQA_data, type == "HR")
CRQA_Resp = subset(CRQA_data, type == "Resp")


#Comparing statistically for HR:
m1 = lm(RR ~ CRQA, data = CRQA_HR)
summary(m1)
m2 = lm(L ~ CRQA, data = CRQA_HR)
summary(m2)
m3 = lm(ENTR ~ CRQA, data = CRQA_HR)
summary(m3)


#Comparing statistically for Resp:
m11 = lm(RR ~ CRQA, data = CRQA_Resp)
summary(m11)
m12 = lm(L ~ CRQA, data = CRQA_Resp)
summary(m12)
m13 = lm(ENTR ~ CRQA, data = CRQA_Resp)
summary(m13)

```
 
### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

prepro_filelist = list.files(pattern = "Study1", path = "PreprocessedAll") # load the preprocessed files

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.

# To set working directory
setwd("/Volumes/Seagate Backup Plus Drive/3 semester/Methods 3/Assignment 4/Assigment 4.2/PreprocessedAll")

# Per each condition
for (co in c("Synchronous","TurnTaking","SelfPaced")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study1_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study1_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study1_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}


#STUDY 2

prepro_filelist = list.files(pattern = "Study2", path = "PreprocessedAll") # load the preprocessed files

num=str_extract_all(prepro_filelist, "\\d+") #extract all numbers in the file name (i.e Study?_G?_T?)

df= as.data.frame(t(as.data.frame(num))) #create a transposed (i.e. "tipped") dataframe of these number
rownames(df)<-NULL #Remove rownames.

pairs=as.numeric(unique(as.numeric(as.character(df$V2)))) #create pairs, i.e. unique group numbers

SurrogateList <- expand.grid(a = pairs, b = pairs) # expand.grid combines all possible combinations of a given vector
SurrogateList = subset(SurrogateList, a != b) # Ensure that pair 1 (i.e group1) doesn't get paired with it self.

# To set working directory
setwd("/Volumes/Seagate Backup Plus Drive/3 semester/Methods 3/Assignment 4/Assigment 4.2/PreprocessedAll")

# Per each condition
for (co in c("Synchronous","TurnTaking","Conversation")){ #loop through a list of condintions 
  for (i in 1:nrow(SurrogateList)){ #and loop through all the pairings of the surrogate list
    
  #start recreate filenames from the working directory based on the matching from the surrogatelist
  f1=paste0('Study2_G',SurrogateList$a[i]) #Insert group numeber from Surrogatelist 
  f2=paste0('Study2_G',SurrogateList$b[i])
  
  file1=prepro_filelist[grepl(f1,prepro_filelist) & grepl(co,prepro_filelist)] #insert conditions as well.
  file2=prepro_filelist[grepl(f2,prepro_filelist) & grepl(co,prepro_filelist)]
  
  d1=read.csv(file1) #Load the recreated filenames
  
  d2=read.csv(file2) 
  
  #Ensure both dataframes have the same length
  if (nrow(d1)>nrow(d2)){
    d1=d1[1:nrow(d2),]
  } else {
    d2=d2[1:nrow(d1),]
  }
  
  #creation of surrogate files. (Riccardo's idea of having fun and completely overdoing it ;-) ) 
  #per each 2 pairs there are 4 possible surrogate pairs: 
  #pair1person1 w pair2person2; 
  d3=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp2,HR1=d1$HR1,HR2=d2$HR2)
  #pair1person2 w pair2person2;
  d4=data.frame(Resp1=d2$Resp1,Resp2=d1$Resp2,HR1=d2$HR1,HR2=d1$HR2)
  
  #pair1person1 w pair2person1;
  d5=data.frame(Resp1=d1$Resp1,Resp2=d2$Resp1,HR1=d1$HR1,HR2=d2$HR1)
  #pair1person2 w pair2person2
  d6=data.frame(Resp1=d2$Resp2,Resp2=d1$Resp2,HR1=d2$HR2,HR2=d1$HR2)
  
  #Make filenames that tells which pairs have been mixed
  file3=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"a_",co,".csv")
  file4=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"b_",co,".csv")
  file5=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"c_",co,".csv")
  file6=paste0("Study2_SurrogateGroup",SurrogateList$a[i],"&",SurrogateList$b[i],"d_",co,".csv")
  
  #write csv files
  write_csv(d3,file.path("surrogate",file3))
  write_csv(d4,file.path("surrogate",file4))
  write_csv(d5,file.path("surrogate",file5))
  write_csv(d6,file.path("surrogate",file6))
  }
}


## Running CRQA:
CRQA = function(data) {
  RespCRQA = crqa(data$Resp1, data$Resp2, delay = 29, embed = 3,
                   radius = 0.8, normalize = 0, rescale = 0,
                   mindiagline = 2, minvertline = 2)
  RespCRQA$RP = NULL  # Remove large matrix
  RespCRQA = as_tibble(RespCRQA) %>%
    mutate(type = 'Resp')
  
  HrCRQA = crqa(data$HR1, data$HR2, delay = 30, embed = 12,
                radius = 2.6, normalize = 0, rescale = 0,
                mindiagline = 2, minvertline = 2)
  HrCRQA$RP = NULL  # Remove large matrix
  HrCRQA = as_tibble(HrCRQA) %>%
    mutate(type = 'HR')
  
  return(rbind(RespCRQA, HrCRQA))
  
}


filelist_surrogate = list.files(path = "surrogate", pattern = ".csv")
CRQA_surrogate = data.frame()
n=1

for (file in filelist_surrogate) {
  d=read_csv(paste0(path = "surrogate/",file))
  
  data=CRQA(d)
  
  data$filename = filelist_surrogate[n]
  
  CRQA_surrogate=rbind(data, CRQA_surrogate)
  
  n=n+1
  
}

CRQA_surrogate$CRQA = "Surrogate"

write.csv(CRQA_surrogate, "CRQA_surrogate.csv")

CRQA_data2 = rbind(crqa_results,CRQA_surrogate)

CRQA_HR2 = subset(CRQA_data2, type == "HR")
CRQA_Resp2 = subset(CRQA_data2, type == "Resp")


#Comparing statistically for HR:
md1 = lm(RR ~ CRQA, data = CRQA_HR2)
summary(md1)
md2 = lm(L ~ CRQA, data = CRQA_HR2)
summary(md2)
md3 = lm(ENTR ~ CRQA, data = CRQA_HR2)
summary(md3)


#Comparing statistically for Resp:
md11 = lm(RR ~ CRQA, data = CRQA_Resp2)
summary(md11)
md12 = lm(L ~ CRQA, data = CRQA_Resp2)
summary(md12)
md13 = lm(ENTR ~ CRQA, data = CRQA_Resp2)
summary(md13)

```
### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?
```{r setup, include=FALSE}

finaldata2_HR = subset(finaldata2, type == "HR")
finaldata2_Resp = subset(finaldata2, type == "Resp")


model1 = lmer(RR ~ Condition + (1|Study), data = finaldata2_HR)
summary(model1)
model2 = lmer(L ~ Condition + (1|Study), data = finaldata2_HR)
summary(model2)
model3 = lmer(ENTR ~ Condition + (1|Study), data = finaldata2_HR)
summary(model3)

model11 = lmer(RR ~ Condition + (1|Study), data = finaldata2_Resp)
summary(model11)
model12 = lmer(L ~ Condition + (1|Study), data = finaldata2_Resp)
summary(model12)
model13 = lmer(ENTR ~ Condition + (1|Study), data = finaldata2_Resp)
summary(model13)

```
### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them